---
title       : Car Selection Application
subtitle    : Best car for your needs!
author      : Sharon Ng
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny, interactive, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
output      : html_document

---

<style>
.title-slide {
  background-color: #FFFFFF; /* #EDE0CF; ; #CA9F9D*/
}

.title-slide hgroup > h1{
 font-family: 'Baskerville', 'Times', serif; 
 font-weight: normal;
}

.title-slide hgroup > h1, 
.title-slide hgroup > h2 {
  font-family: 'Baskerville';
  font-weight: normal;
  color: #000;  /* ; #EF5150*/
}

article p, article li, article li.build, section p, section li{
  font-family: 'Baskerville','Crimson Text', 'Garamond',  'Palatino', sans-serif;
  text-align: justify;
  font-size:22px;
  line-height: 1.5em;
  color: #000;
}

slide:not(.segue) h2{
  font-family: 'Baskerville', Arial, sans-serif;
  font-size: 52px;
  font-style: normal;
  font-weight: normal;
  text-transform: normal;
  letter-spacing: -2px;
  line-height: 1.2em;
/*  color: #193441;*/
/*  color: #02574D;*/
  color: #666;
}
</style>
<h2>Introduction</h2>

<p>This presentation is part of the Course Project for the Coursera Developing Data Products class. The peer assessed assignment has two parts. First, a Shiny application that is deployed on Rstudio's servers. Second, to prepare a reproducible pitch presentation about the application. This presentation is addresses the second requirement and it is made with Slidify. 

<p><a href="https://shibuyume.shinyapps.io/shiny target=_blank">Click here</a> to go to the app developed for the first part of the assignment.

<p><a href="https://github.com/raencinas/dataproducts target=_blank">Source code for ui.R and server.R files are available on the GitHub.</a>

--- 

<h2>Select the best car for your trip App</h2>

* This app helps you to choose a car for a trip, using the mtcars dataset.

* First, you need to inform the distance of your trip and the price of gasoline in your region. These information will be used to calculate the Gasoline Expenditure for each car in the dataset. Then, you can enter the maximum amount of money you want to spend on gasoline, and the table shows only the cars that have Miles per Gallon (mpg) that can go below this value.

* Second, you can choose some Characteristics of the cars that you desire: Cylinders, Displacement, Horse Power and Transmission. The table will show only the cars with the filters selected. You can sort the table according to the variable you want by clicking the arrows at the top of the table.


--- 
<h2>First glance at the mtcars dataset</h2>

* The data used in the app comes from the Motor Trend Car Road Tests (mtcars) dataset. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). 



```{r}

data(mtcars)
head(mtcars)

```

---  

<h2>Plotting relationships</h2>
By using a scatter plot, we can see the relationships of MPG with weight and displacement. 


```{r, warning=FALSE}
library(car)
scatterplotMatrix(~mpg+disp+wt, data=mtcars, cex.axis=1.5)

```

